Logeti, Stockhausen and Koenig:\\Esthetics of Electronic Music

### 2015-07-24 manuscript.tex
Break Stockhausen ideas into subsubsections, add my response

\begin{enumerate}
  \item The correlation of the coloristic, harmonic-melodic, and metric-rhythmic aspects of composition.
  \item The composition and de-composition of timbres.
  \item The characteristic differentiation among degrees of intensity.
  \item The ordered relationships between sound and noise.
\end{enumerate}

>>>>

\subsubsection{The correlation of the coloristic, harmonic-melodic, and metric-rhythmic aspects of composition}
\label{subs:stockhausen:time}

Most of the current paper by Stockhausen deals with this element.
In my opinion, Stockhausen attitude toward the correlation between different compositional aspects could be put by the two following ideas:

\begin{itemize}
    \item He classify different sonic elements as different perceptions of the time domain.
    For example, periodic elements of short time intervals are intercepted as pitch, and therefore as the basis for melody and harmony;
    Periodic elements of medium time interval are intercepted as tempo and rhythm;
    Those of larger time intervals are seen as musical structure.
    Furthermore, Stockhausen describe those ``time spans'' as spread across 7 octaves:
    Pitch is spread across the 7 octaves of the piano;
    Tempo and rhythm are spread from 1/16 of a second up to 8 seconds;
    Lastly, time spans of 8 to 1024 seconds are intercepted as structural building blocks.

    \item Based on the attitude described above Stockhausen approach electronic music as a tool to apply total serializm (TODO: {total serializm reference}).
    Furthermore, he argues that serializm must exist in electronic composition.
    The thinking path the led Stockhausen to this argument is clear, but it is still hard for me to agree with him.
    Later, I will try to confront this idea with those reflected in his and Ligeti's music.
\end{itemize}

Overall, I can not find a common ground between this compository element to those of Ligeti that were mentioned before.
Their attitudes regarding unified perception of time are, most probably, contradicting.

\subsubsection{The composition and de-composition of timbres}
\label{subs:stockhausen:timber}

Ligeti reference this ideas as following:
Modification of timbre and dynamics are obviously very significant but the patterns emerging from them are even more important...
I should say that the changes and modifications of the overall pattern are the important feature, not the tone colors. (Ligeti in conversation, p. 39).

\subsubsection{The characteristic differentiation among degrees of intensity}
\label{subs:stockhausen:intensity}

I'm not sure I fully understand the meaning of this element, not from the current paper, at least.
I will leave this element ``out of scope'' for now.

\subsubsection{The ordered relationships between sound and noise}
\label{subs:stockhausen:noise}

main area to compare Ligeti and Stockhausen ideas TODO.
